### 2014-11-13 tex/intro.tex
boo

In this work, in order to effectively represent multiple heaps
simultaneously in the context of symbolic execution we define a novel
heap representation and an algorithm to initialize and update the heap
on-the-fly. Our summary heap approach supports aliasing, it does not
require constraint rewriting on heap updates, and it reduces the
non-determinism in the search space during symbolic execution.

>>>>

In this work, to effectively represent multiple heaps simultaneously
in the context of symbolic execution we define a novel heap
representation and an algorithm to initialize and update the heap
on-the-fly. Our summary heap approach supports aliasing, it does not
require constraint rewriting on heap updates, and it reduces the
non-determinism in the search space during symbolic execution.
